Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-15 p2/rec-sound.tex
Finished first part of proof

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection is also defined on any filesystem
either of them is defined on:
$\worksm{A}{\acb}$, and, by symmetry,
$\worksm{B}{\acb}$.
\end{mylem}

\begin{proof}
The difficulty is that commands in $\acbnp$ can occur anywhere in $A$.
Therefore, first we prove the following:
if all commands are marked in $A$ that also appear in $B$,
then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.

We show that $A$ can be transformed via equivalences into $A'$ for which this is true.
We know that if the marked commands are not at the beginning, then
the sequence contains an unmarked command followed by a marked command.
We show that these can be swapped resulting in an equivalent sequence.
Then, by repeating this process similarly to bubble sorting, we arrive at 
a suitable $A'$.

@@

In the cases then $\czmwv\cc\cxynv$ is either a construction or a destruction pair,
and, depending on which is the case,
$m=\parent(n)$ or $n=\parent(m)$, respectively.

If $B$ has a command on $m$, let it be $\cqrmv$.
As \cref{simple_distant_pairs} applies to $B$, we know that
$\cxynv$ (which is in $B$), and $\cqrmv$ must also form a construction
or destruction pair.
As $\cxynv$ cannot be both a construction and a destruction command,
this pair must be of the same type as $\czmwv\cc\cxynv$,
and as the relationship between $n$ and $m$ is given,
we know $\cqrmv$ must precede $\cxynv$ in $B$.

@@

The last remaining case is when there is no command on $m$ in $B$.
TODO
TODO

OLD:

If $B$ has no command on $m$, then let $B'$ be $B$, 
but with an extra command added to it just before $\cxynv$
according to \cref{ax_child_assert,ax_parent_assert}, 
from which we know that $B'\equiv B$.
We also know that $B'$ is still minimal (but no longer simple).

In either case, therefore,
we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
Let this command on $m$ be $\cqrmv$.
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
\end{gather*}

Going back to the construction and destruction pairs we see that the output value of the first command
is either $\vald$ or $\empt$ and is determined by the relationship between $n$ and $m$.
If $B$ had no command on $m$,
this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $[z]=[q]=[r]=[w]$, 
but $A$ contained no assertion commands.

We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
are at the beginning, and therefore 
from \cref{worksextpostfix} we know that
$\worksm{A}{\acb}$ and, by symmetry, $\worksm{B}{\acb}$.
\end{proof}

@@

% TODO Set or sequence? See also above

\noindent
We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From the above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksmbx{A,B}{\acb\cc \bma\cc \reca}. \]
We can prove this if we can show that
\[ \worksmbx{A,B}{\acb\cc \reca}. \]
This is because we already know
that $\worksmbx{A,B}{\acb\cc \bma}$ (as $\worksmbx{A,B}{B}$),
which, combined with the above, yields
\[ \worksmbb{A,B}{\acb\cc \reca, \acb\cc \bma}. \]
Also, as $\reca\indep\bma$,
from \cref{indep_prefix_combine}
we know
\[ \worksmbx{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
As $\worksmeqsign$ is transitive, combining the two results
gives the statement we intended to prove.

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
% TODO Inverse is used here - how/why?
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\amb$ to $S$ and $\bma$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksm{\sqs{C}}{S^*}. \]
\end{mylem}

@@

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$ via equivalences
so that all marked commands would be at its beginning.
If so, then 
$\worksm{\sqs{C}}{S^*}$ 
based on \cref{worksextpostfix}
as $\worksm{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

@@

Let therefore the marked command in $S$ be $\cxynv$
and the preceding unmarked command be $\czwmv$.
As $S$ is simple and $\wrks{S}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $S$,
and we show that the other two cases are not possible as they would lead to a contradiction.

>>>>

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences for which $\worksmnilb{A, B}$.
Then $A$ can be separated into their intersection and the remaining commands:
\[ \acb\cc\amb \in \orderset{A}. \]
\end{mylem}

\begin{proof}
We prove that
if all commands are marked in $A$ that also appear in $B$,
then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.

We show that $A$ can be transformed into $A'$ for which this is true.
We know that if the marked commands are not at the beginning, then
the sequence contains an unmarked command followed by a marked command.
We show that these can be swapped resulting in an equivalent sequence.
Then, by repeating this process similarly to bubble sorting, we arrive at 
a suitable permutation of $A$, which is also equivalent to $A$, and therefore in $\orderset{A}$.

@@

In the cases then $\czwmv\cc\cxynv$ is either a construction or a destruction pair,
and, depending on which is the case,
$m=\parent(n)$ or $n=\parent(m)$, respectively.

If $B$ has a command on $m$, let it be $\cqrmv$.
As \cref{simple_distant_pairs} applies to $B$, we know that
$\cxynv$ (which is in $B$), and $\cqrmv$ must also form a construction
or destruction pair.
As $\cxynv$ cannot be both a construction and a destruction command,
this pair must be of the same type as $\czwmv\cc\cxynv$,
and as the relationship between $n$ and $m$ is given,
we know $\cqrmv$ must precede $\cxynv$ in $B$.

@@

The last remaining case is when there is no command on $m$ in $B$.
Let $B'$ be $B$
with an extra assertion command added just before $\cxynv$
according to \cref{ax_child_assert,ax_parent_assert}, 
from which we know that $B'\equiv B$.
Let the new command be $\cqrmv$.
As $B'$ is still minimal (but no longer simple),
the argument above applies, and we again know
that $[q]=[z]$ and $r=w$.
As $\cqrmv$ is an assertion command, $[q]=[r]$ also holds,
from which $[z]=[w]$ (as $[z]=[q]=[r]=[w]$), which is a contradiction
as $A$ contains no assertion commands.
\end{proof}

@@

\noindent
We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksmbx{A,B}{\acb\cc \bma\cc \reca}. \]
We can prove this if we can show that
\[ \worksmbx{A,B}{\acb\cc \reca}. \]
This is because we already know
that $\worksmbx{A,B}{\acb\cc \bma}$ (as $\worksmbx{A,B}{B}$),
which, combined with the above, yields
\[ \worksmbb{A,B}{\acb\cc \reca, \acb\cc \bma}. \]
Also, as $\reca\indep\bma$,
from \cref{indep_prefix_combine}
we know
\[ \worksmbx{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
As $\worksmeqsign$ is transitive, combining the two statement above
gives $\worksmbx{A,B}{B\cc \reca}$, which is what we intend to prove.

\noindent
To restate some results above, we therefore already know the following:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
% TODO Inverse is used here - how/why?
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
TODO HOW IS THIS USED?
\end{itemize}

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\amb$ to $S$, $\reca$ to $S^*$, and $\bma$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksm{\sqs{C}}{S^*}. \]
\end{mylem}

@@

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$
so that all marked commands would be at its beginning.
If so, then 
$\worksm{\sqs{C}}{S^*}$ 
based on \cref{worksextpostfix}
as $\worksm{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

@@

Let therefore the marked command in $S$ be $\cxynv$
and the preceding unmarked command be $\czwmv$.
As $S$ is simple and $\wrks{S}$, from 
\cref{ax_distantrel_breaks,simple_distant_pairs}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $S$,
and we show that the other two cases are not possible as they would lead to a contradiction.
